The Driving Forces of API Evolution

### 2015-05-21 thesis/paper.tex
designer->architect

\begin{abstract}
%Motivation
Evolving an API is a precipitous activity, mainly because of the great implications modifications can have on the users of it. As the usage of APIs increases, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs. 
%Problem
If no attempt at analysing or quantifying the evolution of an API is made, there will be a lacking understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify. We believe, that long-standing software evolution theories can provide additional insight to the field of APIs, and be of great use to companies maintaining APIs. 
%Method
In this case study, we conduct a qualitative investigation on what drives the evolution of an industry company's existing API, by examining two versions of the API code. The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions were tested by interviewing the designer of the API. 
%Results
The results of this analysis show that the largest driving force of API evolution is the desire for new functionality. Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution, in the context of APIs. We also found that change decisions were highly reverse engineerable, and identified the feedback loop of an API to be the most major area of improvement. 
\end{abstract}

@@

%Purpose, general
Modifications to deployed APIs may negatively impact its users. It is therefore important to investigate why these changes occur. Understanding the motives behind the changes could help API designers to  prevent potential future changes to their APIs. Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives. 
%Purpose, case company
Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks for the case company. This improved communication could provide a common language that developers, users and management can use to discuss potential evolution of the APIs. Understanding the evolution theories could further assist understanding of how change will occur and how to plan for it. Lastly, by keeping a history of changes to an API over time, trends can be identified which could help with future API design.

>>>>

\begin{abstract}
%Motivation
Evolving an API is a precipitous activity, mainly because of the great implications modifications can have on the users of it. As the usage of APIs increases, software development organisations must take an empirical and scientific approach to the way they manage the evolution of their APIs. 
%Problem
If no attempt at analysing or quantifying the evolution of an API is made, there will be a lacking understanding of the evolution, and possible improvements to the maintenance strategy will be difficult to identify. We believe, that long-standing software evolution theories can provide additional insight to the field of APIs, and be of great use to companies maintaining APIs. 
%Method
In this case study, we conduct a qualitative investigation on what drives the evolution of an industry company's existing API, by examining two versions of the API code. The changes were analysed based on two software evolution theories, and the extent to which we could reverse engineer the change decisions were tested by interviewing the architect of the API. 
%Results
The results of this analysis show that the largest driving force of API evolution is the desire for new functionality. Our findings which show that changes happen sporadically, rather than continuously, invalidate a law of software evolution, in the context of APIs. We also found that change decisions were highly reverse engineerable, and identified the feedback loop of an API to be the most major area of improvement. 
\end{abstract}

@@

%Purpose, general
Modifications to deployed APIs may negatively impact its users. It is therefore important to investigate why these changes occur. Understanding the motives behind the changes could help API architects to prevent potential future changes to their APIs. Before industry can safely include such information in their feedback loop, we must critically assess to what degree we can reverse engineer such motives. 
%Purpose, case company
Identifying the types of changes that occur when an API evolves will improve communication and discussions regarding maintenance and evolution tasks for the case company. This improved communication could provide a common language that developers, users and management can use to discuss potential evolution of the APIs. Understanding the evolution theories could further assist understanding of how change will occur and how to plan for it. Lastly, by keeping a history of changes to an API over time, trends can be identified which could help with future API design.
